Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-12-16 bbbq_article.tex
For 30 SNPs per gene, we know that TMHs are evolutionarily conserved

The human immune system is unexpectedly attentive towards
human transmembrane helices (TMHs), as TMH-derived peptide fragments
bind to histocompatibility complex (MHC) class I more often then expected
by chance only, which can be mostly explained by the low hydrophobicity
of those residues.
The physiological reason is yet unclear,
yet this finding hints that there has been selection upon detecting TMH-derived
peptides in pathogens.
If this signature of selection is present in MHC-II is unknown.
This study shows that MHC-I [also has/does not have] more
epitopes derived from a TMH for a pathogen proteome, when compared with
a host proteome.
Additionally, MHC-II binds to peptides derived from TMHs 
[less/equally/more] often than expected by chance.
Lastly, we show the TMHs are [more/less/equally] 
conserved by determining if SNPs are found in TMH more/less/equal
than expected by chance.
Our findings suggest that the immune system is [less/neutral/more]
vigilant to TMHs than expected by chance and this has 
left [a clear/a weak/no]
signal in the evolutionary history of the pathogen.
The impact of this is [revolutionary/awesome].

@@

To detect the evolutionary conservation of TMHs, 
we use the follow workflow (also shown
in figure \ref{fig:snp_workflow}) to be able to count the
number of SNPs that occur in TMHs, as well as the number of SNPs
that occur in TMHs by chance.

To do so, we use the 
NCBI (\url{https://www.ncbi.nlm.nih.gov/}) databases:
'gene' to find the gene names of membane proteins, 
'dbSNP' for SNPs associated with those genes
and 'protein' to obtain the sequence of proteins that SNPs act upon.
The 'dbSNP' contains 2 billion (human-only) SNPs, although
it is estimated that approx 10 percent is a false positive 
\richel{see references on dbSNP Wikipedia page}.

@@

>>>>

The human immune system is unexpectedly attentive towards
human transmembrane helices (TMHs), as TMH-derived peptide fragments
bind to histocompatibility complex (MHC) class I more often then expected
by chance only, which can be mostly explained by the low hydrophobicity
of those residues.
The physiological reason is yet unclear,
yet this finding hints that there has been selection upon detecting TMH-derived
peptides in pathogens.
If this signature of selection is present in MHC-II is unknown.
This study shows that MHC-I [also has/does not have] more
epitopes derived from a TMH for a pathogen proteome, when compared with
a host proteome.
Additionally, MHC-II binds to peptides derived from TMHs 
more often than expected by chance.
Lastly, we show the TMHs are evolutionarily more conserved,
as less SNPs are found in TMH than expected by chance.
Our findings suggest that the immune system is more
vigilant to TMHs than expected by chance
and suggests that an evolutionary signal in the evolutionary history of a pathogen
may be found.

@@

To detect the evolutionary conservation of TMHs, 
we use the following workflow (also shown
in figure \ref{fig:snp_workflow}) to be able to count the
number of SNPs that occur in TMHs, as well as the number of SNPs
that occur in TMHs by chance.

To do so, we use the 
NCBI (\url{https://www.ncbi.nlm.nih.gov/}) databases:
'gene' to find the gene names of membrane proteins, 
'dbSNP' (\cite{sachidanandam2001map}) for SNPs associated with those genes
and 'protein' to obtain the sequence of proteins that SNPs act upon.
The 'dbSNP' contains 2 billion (human-only) SNPs, although
it is estimated that approximately ten percent (ranging from 2 to 36 percent) 
are artifacts (\cite{carlson2003additional, cutler2001high, gabriel2002structure, mitchell2004discrepancies, musumeci2010single, reich2003quality}).

@@

Regarding the evolutionary conservation of TMHs using SNPs,
again, it is estimated that approx 8.32 percent
of SNPs is caused, due to sequence variations in
highly similar duplicated sequences \cite{musumeci2010single}.
We assume that these duplications occur as often in TMHs as in
regions around these, hence we expect this not to affect our results.
